An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-22 EconGrowthSeminar.Rnw
Added a frame for Saudi Arabia CD coefficients and curve fit.

\begin{frame}{Energy is Essential for Economic Activity} %----------------------------
  What do you do that doesn't require energy?
\end{frame}

@@

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{pprint(cdZA["CD", "lambda"])} & \Sexpr{cdZA["CD", "alpha"]} & \Sexpr{cdZA["CD", "beta"]} & \Sexpr{pprint(cdZA["CD", "gamma"])}\\
            \hline
            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdxZA["CD", "beta"])} & \Sexpr{cdxZA["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{ZA}{0.055}
\end{frame}

>>>>

\begin{frame}{Energy is Essential for Economic Activity} %----------------------------
  \begin{center}What do you do that doesn't require energy?\end{center}
\end{frame}

@@

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{pprint(cdZA["CD", "lambda"])} & \Sexpr{cdZA["CD", "alpha"]} & \Sexpr{cdZA["CD", "beta"]} & \Sexpr{pprint(cdZA["CD", "gamma"])}\\
            \hline
            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdqZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdxZA["CD", "beta"])} & \Sexpr{cdxZA["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_ZA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{ZA}{0.055}
\end{frame}

<<Coefs_SA_CD>>=
cdSA <- cobbDouglasData("SA")
cdqSA <- cobbDouglasData("SA", "Q")
cdxSA <- cobbDouglasData("SA", "X")
@
\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
  \begin{columns}[c]
    \column{2.2in}
      \begin{center}
        \cdeEqn
        \vspace{\baselineskip}

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{cdSA["CD", "lambda"]} & \Sexpr{cdSA["CD", "alpha"]} & \Sexpr{cdSA["CD", "beta"]} & \Sexpr{cdSA["CD", "gamma"]}\\
            \hline
            $q$   & \Sexpr{cdqSA["CD", "lambda"]} & \Sexpr{cdqSA["CD", "alpha"]} & \Sexpr{cdqSA["CD", "beta"]} & \Sexpr{cdqSA["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxSA["CD", "lambda"]} & \Sexpr{cdxSA["CD", "alpha"]} & \Sexpr{cdxSA["CD", "beta"]} & \Sexpr{cdxSA["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_SA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{SA}{0.055}
\end{frame}
